---
title: "625_final_project"
author: "Jiaxin Qian"
date: "11/15/2021"
output: html_document
---

# Read-in data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(srvyr)
library(corrplot)
library(ggplot2)
library(srvyr)
library(Hmisc)

```


```{r}
imp_data <- read.csv("imputation_data1130.csv")
```



use transcan to imput NA

COVID: CVDDIAG_A(13856 ), COVIDTEST_A(13856) 
Access to care (related to covid): DLYCARE_A(13856), DNGCARE_A(13856), VIRAPP12M_A(13856 )
Family care due to covid: HOMECAREDG_A(13856) FAMCAREDNG_A(13856)

```{r}
covid_related <- c("CVDDIAG_A", "COVIDTEST_A", "DLYCARE_A", "DNGCARE_A", "VIRAPP12M_A", "HOMECAREDG_A", "FAMCAREDNG_A")
```


```{r}
imp_data[covid_related] <- lapply(imp_data[covid_related], factor) 

#table(imp_data$FAMCAREDNG_A)
```

#(fmla <- as.formula(paste(" ~ ", paste(covid_related, collapse=" +"))))


```{r}
impute_arg_full <- aregImpute(~ CVDDIAG_A + COVIDTEST_A + DLYCARE_A + DNGCARE_A + VIRAPP12M_A + HOMECAREDG_A + FAMCAREDNG_A, data = imp_data, n.impute = 5)
impute_arg_full
```

Get the imputed values for these 7 variables, each varirable has 5 imputations
```{r}
na_imp <- impute_arg_full$imputed
```

get the imputation matrix for each variable
```{r}
imp_CVDDIAG_A <- impute_arg_full$imputed$CVDDIAG_A
imp_COVIDTEST_A <- impute_arg_full$imputed$COVIDTEST_A
imp_DLYCARE_A <- impute_arg_full$imputed$DLYCARE_A
imp_DNGCARE_A <- impute_arg_full$imputed$DNGCARE_A
imp_VIRAPP12M_A <- impute_arg_full$imputed$VIRAPP12M_A
imp_HOMECAREDG_A <- impute_arg_full$imputed$HOMECAREDG_A
imp_FAMCAREDNG_A <- impute_arg_full$imputed$FAMCAREDNG_A
```

maybe get the mode?
```{r}
imp_CVDDIAG_A[which(rowSums(imp_CVDDIAG_A)<8),]


```

```{r}
imp_CVDDIAG_A["2621",]
```

