---
title: "625_final_project"
author: "Jiaxin Qian"
date: "11/15/2021"
output: html_document
---

# Read-in data
```{r setup, include=FALSE}
library(tidyverse)
library(srvyr)
library(corrplot)
library(ggplot2)
library(srvyr)
library(Hmisc)

```


```{r}
imp_data <- read.csv("imputation_data1130.csv")

```



use aregimpute to imput NA

COVID: CVDDIAG_A(13856 ), COVIDTEST_A(13856) 
Access to care (related to covid): DLYCARE_A(13856), DNGCARE_A(13856), VIRAPP12M_A(13856 )
Family care due to covid: HOMECAREDG_A(13856) FAMCAREDNG_A(13856)

```{r}
covid_related <- c("CVDDIAG_A", "COVIDTEST_A", "DLYCARE_A", "DNGCARE_A", "VIRAPP12M_A", "HOMECAREDG_A", "FAMCAREDNG_A")
```


```{r}
imp_data[covid_related] <- lapply(imp_data[covid_related], factor) 

#table(imp_data$FAMCAREDNG_A)
```

#(fmla <- as.formula(paste(" ~ ", paste(covid_related, collapse=" +"))))


```{r}
impute_arg_full <- aregImpute(~ CVDDIAG_A + COVIDTEST_A + DLYCARE_A + DNGCARE_A + VIRAPP12M_A + HOMECAREDG_A + FAMCAREDNG_A ,data = imp_data, tlinear = FALSE, n.impute = 5)

```

# Get the imputed values
```{r}
imputed <-impute.transcan(impute_arg_full, data=imp_data, imputation=1, list.out=TRUE, pr=FALSE, check=FALSE)
```


# convert the list to the database
```{r}
imputed.data <- as.data.frame(do.call(cbind,imputed))
```

# arrange the columns accordingly
```{r}
imp_data[, colnames(imputed.data)] <- imputed.data
```


```{r}
write.csv(imp_data, file = "imp_data1.csv")
```


repeat the same procedure for the rest of imputations
```{r}
imputed2 <-impute.transcan(impute_arg_full, data=imp_data, imputation=2, list.out=TRUE, pr=FALSE, check=FALSE)
imputed.data2 <- as.data.frame(do.call(cbind,imputed2))
imp_data[, colnames(imputed.data2)] <- imputed.data2
write.csv(imp_data, file = "imp_data2.csv")
```



```{r}
imputed3 <-impute.transcan(impute_arg_full, data=imp_data, imputation=3, list.out=TRUE, pr=FALSE, check=FALSE)
imputed.data3 <- as.data.frame(do.call(cbind,imputed3))
imp_data[, colnames(imputed.data3)] <- imputed.data3
write.csv(imp_data, file = "imp_data3.csv")
```

```{r}
imputed4 <-impute.transcan(impute_arg_full, data=imp_data, imputation=4, list.out=TRUE, pr=FALSE, check=FALSE)
imputed.data4 <- as.data.frame(do.call(cbind,imputed4))
imp_data[, colnames(imputed.data4)] <- imputed.data4
write.csv(imp_data, file = "imp_data4.csv")
```


```{r}
imputed5 <-impute.transcan(impute_arg_full, data=imp_data, imputation=5, list.out=TRUE, pr=FALSE, check=FALSE)
imputed.data5 <- as.data.frame(do.call(cbind,imputed5))
imp_data[, colnames(imputed.data5)] <- imputed.data5
write.csv(imp_data, file = "imp_data5.csv")
```


```{r}
sum(is.na(imp_data[, colnames(imputed.data5)]))
```

